### 2021-09-10 sections/healthcare_application/main.tex
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

The system defined in section \ref{sec:model_overview} can be directly applied 
to a healthcare scenario with two such queueing systems.
The two queueing systems can be thought of as two Emergency Departments (ED) and 
the Emergency Medical Services (EMS) as a distributor that distributes 
patients to them.
The parameters of the model can also be mapped into parameters of the ED and 
the EMS.

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\)
    \item \( \mu_i \): The service rate of patients at ED \(i\)
    \item \( C_i \): The number of available resources (beds) in ED \(i\)  
    \item \( T_i \): The strategy that ED \(i\) chooses to play
    \item \( N_i \): The total patient capacity of ED \(i\)
    \item \( M_i \): The total parking capacity of ED \(i\)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Importance} of blocking time and 
    lost individuals (equation \ref{eq:obj-distributor})
\end{itemize}

@@

The game to be played now is between the two EDs and the EMS. 
The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the blocking time of ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect-info-game}).

\subsection{Data Analysis}

@@

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for these particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@

To study the efficiency of the strategies being played a new concept is 
introduced that considers the ratio between each hospital's best achievable 
blocking time and the one that is being played.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(\tilde{s})\), where 
\(i \in [1, 2]\) to distinguish among the two players/hospitals where 
\(\tilde{s}\) is the strategy that is being played by player \( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
is given by:

@@

\textbf{Base run:}
Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics the game can be simulated and show the compartmentalised price of 
anarchy at every iteration for both players.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.

@@

It can be observed that the learning algorithm reaches a stable pair of 
strategies where \(T_1 = 5\) and \(T_2 = 6\). After a number of iterations the
price of anarchy for both players stabilises and barely increases until the 
final iteration.

\textbf{Increasing \(\lambda_2\):}
Figure \ref{fig:ard_lambda_2} shows a similar run of the
algorithm but when the strategies begin to stabilise a huge increase in the
arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes more efficient. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) leaves 
less potential for improvement.

@@

\textbf{Incentivising players:}
From figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it can be
seen that we can change some parameters of the model to make it more efficient.
The approach used on figure \ref{fig:ard_penalty} is slightly different than 
the previous cases.
Once the played strategies in asymmetric replicator dynamics strategies 
converge the payoff matrices of the two are scaled in such a way so that the 
utilities of the selected strategy is penalised.

>>>>

The system defined in section \ref{sec:model_overview} can be applied 
to a healthcare scenario with two such queueing systems.
The two queueing systems can be thought of as two Emergency Departments (ED) and 
the Emergency Medical Services (EMS) as a distributor that distributes 
patients to them.
The parameters of the model correspond to the following parameters of the ED and 
the EMS:

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\in\{1, 2\}\)
    \item \( \mu_i \): The service rate of patients at ED \(i\in\{1, 2\}\)
    \item \( C_i \): The number of available resources (beds) in ED \(i\in\{1, 2\}\)  
    \item \( T_i \): The action that ED \(i\in\{1, 2\\) chooses to play which corresponds to the threshold at which they do not accept EMS patients.
    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\\)
    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\\)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
    lost individuals (equation \ref{eq:obj-distributor})
\end{itemize}

@@

The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the blocking time of ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect-info-game}). This corresponds to reacting to experienced delays.

\subsection{Numerical Results}

@@

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for this particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@

To study the efficiency of the strategies being played a new concept is 
introduced that considers the ratio between each hospital's best achievable 
blocking time and the one that is being played.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(\tilde{s})\), where 
\(i \in \{1, 2\}\) to distinguish among the two players/hospitals where 
\(\tilde{s}\) is the strategy that is being played by player \( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
is given by:

@@

\textbf{Initial scenario:}
Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics the emergent behaviour can be measured and the compartmentalised price of 
anarchy at every iteration for both players.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.

@@

The learning algorithm reaches a stable pair of 
strategies where \(T_1 = 5\) and \(T_2 = 6\). After a number of iterations the
price of anarchy for both players stabilises and barely increases until the 
final iteration.

\textbf{Increasing \(\lambda_2\):}
Figure \ref{fig:ard_lambda_2} shows a similar run of the
algorithm but when the strategies begin to stabilise an increase in the
arrival rate of ambulances occurs (i.e \( \lambda_2 = 10.7 \)).

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes more efficient. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) leaves 
the system unable to cope regardless of the decisions made.

@@

\textbf{Incentivising players:}
From figures \ref{fig:ard_lambda_2} and \ref{fig:ard_num_of_servers} it can be
seen that we can change some parameters of the model to make it more efficient.
The approach used on figure \ref{fig:ard_penalty} is slightly different than 
the previous cases.
Once the played strategies in asymmetric replicator dynamics strategies 
converge the payoff matrices of the two are scaled in such a way so that the 
utilities of the selected strategy are penalised. This corresponds to a precise
policy change where more societally beneficial behaviours are incentivised.
